\pretextualchapter{Publications}
\begin{sloppypar}

\noindent Earlier versions of the work in this thesis were published as listed below:

\begin{itemize}

\item \textbf{Studying the Impact of Switching to a Rapid Release Cycle on
Integration Delay of Addressed Issues - An Empirical Study of the Mozilla
Firefox Project.} 
\underline{Daniel Alencar da
	Costa}, Shane McIntosh, Uir\'{a} Kulesza,
	and Ahmed E. Hassan. In Proceedings of the 13th International
Conference on Mining Software Repositories (MSR) , 2016, pp. 374--385.\\
\faTrophy {\em Received the ACM SIGSOFT distinguished paper award} \faTrophy

\item \textbf{An Empirical Study of Delays in the Integration of Addressed
Issues.} \underline{Daniel Alencar da Costa}, Shane McIntosh, Surafel Lemma Abebe,
Uir\'{a} Kulesza, and Ahmed E. Hassan. In Proceedings of the 30th International
Conference on Software Maintenance and Evolution (ICSME), 2014, pp. 281--290.\\
\faTrophy {\em Nominated for best paper award} \faTrophy

\end{itemize}

\noindent The following publications are not directly related to the work that
is presented in this thesis. Instead, they were produced in parallel to the
research performed in this thesis.

\begin{itemize}

\item \textbf{A Framework for Evaluating the Results of the SZZ Approach for
	Identifying Bug-Introducing Changes.} \underline{Daniel Alencar da
	Costa}, Shane McIntosh, Weiyi Shang, Uir\'{a} Kulesza, Roberta Coelho,
	and Ahmed E. Hassan. In the Transactions of Software Engineering Journal
	(TSE), 2016, 18 pages.

\item \textbf{How does the Shift to GitHub Impact Project Collaboration?} Luiz
	Felipe Dias, Igor Steinmacher, Gustavo Pinto, \underline{Daniel Alencar
	da Costa}, and Marco Gerosa. In the 32nd International Conference on
	Software Maintenance and Evolution (ICSME-ERA), 2016, 5 pages.

\item \textbf{Unveiling Developers Contributions Behind Code Commits: An
	Exploratory Study.} \underline{Daniel Alencar da Costa}, Uir\'{a} Kulesza, Eduardo Aranha,
	and Roberta Coelho. In Proceedings of the 29th Annual ACM Symposium on Applied
	Computing (SAC), 2014, pp. 1152--1157.

\item \textbf{Assessing and Evolving a Domain Specific Language for Formalizing Software
	Engineering Experiments: An Empirical Study.} Mar\'{i}lia Freire, Uir\'{a}
	Kulesza, Eduardo Aranha, Gustavo Nery, \underline{Daniel Alencar da Costa},
	Andreas Jedlitschka, Edmilson Campos, Silvia Acu\~{n}a, and Marta G\'{o}mez.
	International Journal of Software Engineering and Knowledge Engineering
	(IJSEKE), 2014, pp. 1509--1531.

\item 

\end{itemize}

\end{sloppypar}
\newpage

